% Berthy Feng's Resume
% Created: 8/25/2017
% Last Modified: 8/25/2017

\documentclass[12pt]{my_resume}

\usepackage[utf8]{inputenc}

\begin{document}
%---------------------------------------------------------------------------
% Header: Name and contact info
\name{Berthy T. Feng}
\vspace{-6pt}
\contact{bfeng@princeton.edu}{(440) 799-9501}{GitHub: berthyf96}

%---------------------------------------------------------------------------
% EDUCATION
\section{Education}

% Princeton University
\begin{resitem}{Princeton University}{Princeton, NJ, Class of 2019}
  \item BSE Candidate in Computer Science, GPA: 3.89 / 4.0
  \item Selected Courses: \textit{Algorithms and Data Structures, %
  Programming Systems, Reasoning about Computation, Computer Vision, %
  Computer Science: An Interdisciplinary Approach, Computer Music}
\end{resitem}

\vspace{-8pt}

% Laurel School
\begin{resitem}{Laurel School}{Shaker Heights, OH, Class of 2015}
  \item Lyman Prize (Valedictorian), Phi Beta Kappa Award, %
  National Merit Finalist, Ohio State Champion in %
  U.S. Extemporaneous Speaking, Quarterfinalist at National Speech \& %
  Debate Tournament
\end{resitem}

%---------------------------------------------------------------------------
% TECHNICAL SKILLS
\section{Technical Skills}

\vspace{-6pt}
\begin{tabular}{l l}%
Programming Languages: & Java, Python, C, C++, Objective-C++, Swift\\
Data Analysis: & R, Stata\\
Additional Tools: & Django, Git, Max/MSP\\
\end{tabular}

%---------------------------------------------------------------------------
% WORK EXPERIENCE
\section{Work Experience}

% Professor Claire Gmachl
\begin{resitem}{Professor Claire Gmachl (Electrical Engineering), Research %
Assistant}{Princeton, NJ, Summer 2017}
  \item Created Pixplor, an “intelligent photo album” iPad app for %
  nursing-home residents with dementia. Pixplor learns user preferences %
  to recommend photos from a database of 5+ million images.
  \item Developed computer vision and machine learning components, %
  including emotion recognition, gaze tracking, and recommendation %
  algorithm.
  \item Wrote server-side code to process client requests using Django %
  REST framework.
  \item Wrote client-side code in Swift and Objective-C++.
  \item Will continue to improve the app after introducing it in local %
  nursing homes and memory care centers.
\end{resitem}

\vspace{-8pt}

% Longbow Research
\begin{resitem}{Longbow Research, Equity Research Intern}%
{Cleveland, OH, Summer 2014 / Winter 2016}
  \item Developed earnings model to forecast Fossil Group's two-year %
  stock performance.
  \item Researched foodservice equipment companies to lay groundwork %
  for analyst coverage.
\end{resitem}

\vspace{-8pt}

% Senate Banking Committee
\begin{resitem}{U.S. Senate Banking Committee, Policy Intern}%
{Washington, DC, Summer 2016}
  \item Collaborated with national security policy team of Senator %
  Sherrod Brown's staff on U.S. Senate Committee on Banking, Housing, and %
  Urban Affairs.
  \item Researched and drafted reports on money laundering and human %
  trafficking.
\end{resitem}

%---------------------------------------------------------------------------
% SELECTED PROJECTS
\section{Selected Projects}

% 3LS Website
\begin{resitem}{3L Solutions Website %
(\url{berthyfeng.com/3ls-website})}{Summer 2017}
  \item Created website for powdered metal tooling company using %
  Bootstrap HTML/CSS/JavaScript framework.
\end{resitem}

\vspace{-8pt}

% Emotionally Intelligent Slideshow
\begin{resitem}{Emotionally Intelligent Slideshow %
(\url{https://github.com/berthyf96/SlideshowDemo})}{Summer 2017}
  \item Created a demo for Pixplor of an iOS app that allows users to %
  flip through pictures while generating user response data, including %
  emotion as recognized from a real-time camera feed of the user’s face.
  \item Wrote an Objective-C++ wrapper class to allow use of OpenCV %
  library in Swift.
\end{resitem}

\vspace{-8pt}

% Drum Pad
\begin{resitem}{Drum Pad (\url{https://github.com/berthyf96/sampling_pad})}%
{Spring 2016}
  \item Created a sampler (drum pad) for musicians to upload audio %
  samples and play the pad as an instrument.
  \item Used piezoelectric sensors to send touch pressure data to an %
  Arduino script and Max/MSP patch.
\end{resitem}

%---------------------------------------------------------------------------
% LEADERSHIP AND ACTIVITIES
\section{Leadership and Activities}

% COS 126 Grader
\begin{resitem}{Princeton CS Department, Undergraduate Grader}%
{Fall 2017 -- present}
  \item Grade assignments in introductory CS course and %
  provide constructive feedback to students.
\end{resitem}

\vspace{-8pt}

% HackPrinceton
\begin{resitem}{HackPrinceton, Marketing Director (Organizer pre-2017)}%
{Fall 2016 -- present}
  \item Lead Marketing team to promote semiannual, 500+ student hackathon %
  to students, sponsors, and mentors.
  \item Volunteered on dev team to refactor HackPrinceton’s website code. %
\end{resitem}

\vspace{-8pt}

% Music Production
\begin{resitem}{Music Production %
(\url{https://soundcloud.com/berthy-feng-1})}{}
  \item Produce electronic music using a mix of audio recording, %
  analog synthesis, and digital synthesis.
\end{resitem}

\end{document}
